A hybrid approach for news recommender system using optimization methods

### 2021-02-25 paper/paper.tex
stated evaluation part

>>>>

    For evaluation we have information about what recommendation list was given to each user, and what is the source of the recommendation:

    \begin{table}[h]
        \centering
        \begin{tabular}{cccc}
            \toprule
            \textit{user\_id} & \textit{recommendation\_list}       & \textit{content\_based\_filtering}  & \textit{collaborative\_filtering} \\
            \midrule
            2 & \{(2, 0.91), (1, 0.74), (3, 0.23)\} & \{(2, 0.45), (1, 0.54), (3, 0.08)\} & \{(2, 0.92), (1, 0.4), (3, 0.3)\}\\

            1 & \{(3, 0.73), (1, 0.69), (2, 0.15)\} & \{(2, 0.6), (1, 0.44), (3, 0.04)\} & \{(2, 0.58), (1, 0.58), (3, 0.14)\}\\
            \vdots & \vdots & \vdots & \vdots \\
            \bottomrule
        \end{tabular}%

        \caption{recommendations' logs}
        \label{tab:recommendation_logs}
    \end{table}

    \begin{itemize}
        \item \textit{recommendation\_list}: list of recommendations that consists of pairs (\textit{item\_id}, \textit{score})
        \item \textit{content\_based\_filtering} \& \textit{collaborative\_filtering}: sources of recommendation
    \end{itemize}

    As we use weighted sum of our recommmenders, we have unique boost values for every user:

    \begin{table}[h]
        \centering
        \begin{tabular}{ccc}
            \toprule
            \textit{user\_id} & \textit{content\_based\_filtering} & \textit{collaborative\_filtering} \\
            \midrule
            1                 & 0.25                                  & 1                               \\
            2                 & 1                               & 0.5                                \\
            \vdots & \vdots & \vdots \\
            \bottomrule
            \end{tabular}%
        \caption{boost values}
        \label{tab:boost_values}
    \end{table}

    To illustrate score calculation of recommendations, take a look at 1st row of table \hyperref[tab:recommendation_logs]{recommendations' logs}. We see recommendation $r = \{(2, 0.91), (1, 0.74), (3, 0.23)\}$ for user $u = 2$, so we should find boost values for this particular user in table \hyperref[tab:boost_values]{boost values}: content-based filtering boost $b_{cbf}$ for $u$ is $1$, collaborative filtering boost $b_{cf}$ is $0.5$. So final score is calculated in the following way: $0.91 = 0.45 * b_{cbf} + 0.92 * b_{cf} = 0.45 * 1 + 0.92 * 0.5 = 0.45 + 0.46$.

    Also we have information about \hyperref[tab:show]{shows} and \hyperref[tab:view]{views}, so we are able to track what item in recommendation list was clicked and what item was skipped, so depending on this information we can track if user liked item or not.
